---
title: "Problem 2"

output: 
  html_document:
    toc: true
    toc_float: true
    theme: flatly
---

***

Here I will create a flexdashboard using *plotly* for three distinct plot types.

***

```{r setup, include = FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(viridis)
library(dplyr)
library(p8105.datasets)

library(plotly)
```

## Data

The dataset that I choose to do is ["*NY Restaurant Inspectations*"](https://dev.socrata.com/foundry/data.cityofnewyork.us/43nn-pn8j), which is information on restaurant name and location, type of food, inspection date, and details on violation codes, total scores, and associated grades. 

***

## Plotly Boxplot

Using a boxplot to indicate the **score** distribution in all restaurants in different *boroughs*.

```{r message=FALSE, echo=FALSE, warning=FALSE}
# read in data
data("rest_inspec")

rest_inspec %>% 
  select(boro, score, cuisine_description) %>% 
  mutate(boro = fct_reorder(boro, score)) %>% 
  filter(boro != "Missing") %>% 
  plot_ly(y = ~score, color = ~boro, type = "box",
          colors = "Set2")
```

***

## Plotly Barplot

Using a barplot to indicate the **number** of top 15 restaurants in *Manhattan*.

```{r message=FALSE, echo=FALSE, warning=FALSE}
rest_inspec %>% 
  select(boro, cuisine_description) %>% 
  filter(boro == "MANHATTAN") %>%
  count(cuisine_description, sort = TRUE) %>% 
  top_n(15) %>% 
  mutate(cuisine_description = 
           recode(cuisine_description, "Latin (Cuban, Dominican, Puerto Rican, South & Central American)" = "Latin (CDPRSCA)")) %>% 
  mutate(cuisine_description = fct_reorder(cuisine_description, n)) %>% 
  plot_ly(x = ~cuisine_description, y = ~n, 
          color = ~cuisine_description, type = "bar") %>% 
  layout(
    title = "Number of Top 15 Cuisine Restaurants in Manhattan",
    xaxis = list(title = "Cuisine Description"),
    yaxis = list(title = "Number")
  )
```

***

## Line Plot

